PANCHANGE_data_preprocessing

### 2020-09-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
added comment about edgi ocir coping missing ID

edgi data frame list
```{r edgi data frame list}
if(EDGI == TRUE) {
dfs.list <- list(
  dem.raw.id,
  edgi.employment.coping.ocir,
  mhd.raw.categories,
  prepan.gad.raw.id,
  prepan.pcl.raw.id,
  prepan.phq.raw.id,
  prepan.ocir.raw.id,
  coping.gad.raw.id,
  coping.pcl.raw.id,
  coping.phq.raw.id,
#  coping.ocir.raw.id,
  als.raw.id,
  ess.raw.id,
  midas.raw.id,
  nmss.raw.id,
  nmsw.raw.id,
  tinnitus.raw.id
)
}
```

>>>>

edgi data frame list
```{r edgi data frame list}
if(EDGI == TRUE) {
dfs.list <- list(
  dem.raw.id,
  edgi.employment.coping.ocir,
  mhd.raw.categories,
  prepan.gad.raw.id,
  prepan.pcl.raw.id,
  prepan.phq.raw.id,
  prepan.ocir.raw.id,
  coping.gad.raw.id,
  coping.pcl.raw.id,
  coping.phq.raw.id,
#  coping.ocir.raw.id, # joint in the chunk before because it was missing the EDGI ID in any column
  als.raw.id,
  ess.raw.id,
  midas.raw.id,
  nmss.raw.id,
  nmsw.raw.id,
  tinnitus.raw.id
)
}
```
